Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-16 article/article.tex
(+) small par on mcts

\subsection{Monte Carlo tree search overview}
Monte-Carlo is a best-first search method using stochastic simulations. It is
composed of four phases, namely
\begin{compactenum}
	\item selection,
	\item expansion,
	\item simulation,
	\item backpropagation.
\end{compactenum}
Those phases are repeated until a stopping criterium is reached,
see\ref{alg:gen_mcts} (memory usage or time).
\begin{algorithm}
	\caption{General MCTS~\cite{browne2012survey}}\label{alg:gen_mcts}
	\begin{algorithmic}
		\Procedure{MctsSearchTree}{$v_0$}
		\While{within computational budget}
		\State{} \([v^l_1, \dots, v^l_i] \gets\) \Call{TreePolicy}{$v_0$}
		\State{} \(\Delta \gets\) \Call{DefaultPolicy}{$v^l_i$}
		\State{} \(r \gets\) \Call{Reward}{$\Delta$}
		\State{} \Call{Backup}{$[v^l_1, \dots, v^l_i]$, $r$}
		\EndWhile{}
		\EndProcedure{}
	\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Monte Carlo tree search}
\subsubsection{Overview}
Monte-Carlo is a best-first search method using stochastic simulations. The
algorithm actually uses two trees, an underlying tree associated to the model
(e.g.\ a game tree) and a search tree. The latter is built incrementally by the
algorithm the following way, at each step, starting from the root, the most
promising nodes towards the bottom of the tree are selected. Once a leaf of the
search tree is reached, a new node coming from the model tree is added to the
leaf. A simulation is then run from this newly added node to evaluate the
outcome of a path starting from it. The result of the simulation is eventually
backpropagated to the consecutive fathers of the new node.
\begin{compactenum}
	\item selection,
	\item expansion,
	\item simulation,
	\item backpropagation.
\end{compactenum}
Those phases are repeated until a stopping criterium is reached,
see\ref{alg:gen_mcts} (memory usage or time).
\begin{algorithm}
	\caption{General MCTS~\cite{browne2012survey}}\label{alg:gen_mcts}
	\begin{algorithmic}
		\Procedure{MctsSearchTree}{$v_0$}
		\While{within computational budget}
		\State{} \([v^l_1, \dots, v^l_i] \gets\) \Call{TreePolicy}{$v_0$}
		\State{} \(\Delta \gets\) \Call{DefaultPolicy}{$v^l_i$}
		\State{} \(r \gets\) \Call{Reward}{$\Delta$}
		\State{} \Call{Backup}{$[v^l_1, \dots, v^l_i]$, $r$}
		\EndWhile{}
		\EndProcedure{}
	\end{algorithmic}
\end{algorithm}
